### 2013-07-22 doc/asplos14/memory.tex
Fix access API, use `description` env for API's throughout

\begin{figure}[htbp]
  \begin{center}
    \begin{minipage}{\columnwidth}
	\small
	\begin{tabular}{l}
      	\texttt{\scriptsize GlobalAddress<T> global\_malloc<T>( size )} \\
      	\texttt{\scriptsize global\_free( GlobalAddress<T> )} \\ 
      	Allocation in the global heap \\ \\
      	\texttt{\scriptsize delegate\_read( GlobalAddress<T>, T )}  \\
      	\texttt{\scriptsize delegate\_read\_async( GlobalAddress<T>, T )}  \\
      	\texttt{\scriptsize delegate\_write( GlobalAddress<T>, T value)} \\
      	\texttt{\scriptsize delegate\_write\_async( GlobalAddress<T>, T )} \\
      	\texttt{\scriptsize delegate\_cas( GlobalAddress<T>, T, T )} \\
      	\texttt{\scriptsize delegate\_fetch\_inc( GlobalAddress<T>, T )} \\
      	\texttt{\scriptsize delegate\_fetch\_inc\_async( GlobalAddress<T>, T )} \\ 
      	Memory operations at the home core of a global address \\ \\
      	\texttt{\scriptsize buffer\_acquire( GlobalAddress<T>, local\_buf, \{RO,RW,WO\})} \\
      	\texttt{\scriptsize buffer\_release( GlobalAddress<T>, local\_buf )} \\ 
		Perform buffer operations to acquire/release global data.  \\
		Acquire copies all data to local node and returns a pointer. \\ 	
		For write acquire, release copies data back to global memory. \\
	\end{tabular}
      \caption{\label{fig:accessing-memory} \Grappa API for memory accesses.}     \end{minipage}
  \end{center}
\end{figure}

>>>>

\begin{figure}[htbp]
  \begin{center}
    \begin{minipage}{0.95\columnwidth}
	\small
  \begin{description}
    \item[Allocation in the global heap:] \hfill \\
      	\lstinline[style=grappa]{GlobalAddress<T> global_malloc<T>( size )} \hfill \\
      	\lstinline[style=grappa]{global_free( GlobalAddress<T> )}  \hfill
    \item[Delegate operations:] \emph{(at the owning core of a global address)} \hfill \\
      	\lstinline|T    delegate_read( GlobalAddress<T>)|  \hfill \\
      	\lstinline|void delegate_write( GlobalAddress<T>, T value)| \hfill \\
      	\lstinline|void delegate_write_async( GlobalAddress<T>, T value)| \hfill \\
      	\lstinline|bool delegate_cas( GlobalAddress<T>, T cmp, T set)| \hfill \\
      	\lstinline|T    delegate_fetch_inc( GlobalAddress<T>, T inc)| \hfill \\
      	\lstinline|void delegate_inc_async( GlobalAddress<T>, T inc)|  \hfill\\ 
        \lstinline|void buffer_acquire( GlobalAddress<T>, T * local_buf, {RO,RW,WO})| \hfill \\
        \lstinline|void buffer_release( GlobalAddress<T>, T * local_buf )| \hfill
    % Perform buffer operations to acquire/release global data.
    % Acquire copies all data to local node and returns a pointer.
    % For write acquire, release copies data back to global memory.
	\end{description}
      \caption{\label{fig:accessing-memory} \Grappa API for memory accesses.}     \end{minipage}
  \end{center}
\end{figure}

### 2013-07-22 doc/asplos14/tasks.tex
Fix access API, use `description` env for API's throughout

\paragraph{Workers} Workers execute application and system (e.g.,
communication) tasks. A worker is simply a collection of status bits and a
stack, allocated at a particular core. When a task is ready to execute it
is assigned to a worker, that executes the task functor on its own stack. 
Once a task is mapped to a worker it stays with that worker until it finishes.

\paragraph{Scheduling} During execution, a worker yields control of its core
whenever performing a long-latency operation, allowing the processor to
remain busy while waiting for the operation to complete. In addition, a
programmer can direct scheduling explicitly via the \Grappa API calls shown in
Figure~\ref{fig:scheduling}. To minimize yield overhead, the \Grappa scheduler
operates entirely in user-space and does little more than store state of one
worker and load that of another.

\TODO{either explain the usage of yield vs suspend in talking about
    short and longer latency tolerance or eliminate the
    distinction}
\begin{figure}[htbp]
  \begin{center}
	\begin{tabular}{l}
    \texttt{\scriptsize yield() } \\
      Yields core to scheduler, enqueuing caller to be \\ scheduled again soon \\
    \texttt{\scriptsize wake( task * $t$ ) } \\
      Enqueues some other task $t$ to be scheduled again soon \\
    \texttt{\scriptsize suspend() }  \\
      Yields core to scheduler, enqueuing caller only once \\ another task calls wake \\
	\end{tabular}
    \begin{minipage}{0.95\columnwidth}
      \caption{\label{fig:scheduling} \Grappa scheduling API } 
    \end{minipage}
  \end{center}
\end{figure}

@@

\begin{figure}[htbp]
  \begin{center}
	\begin{tabular}{l}
    \texttt{\scriptsize spawn( Functor f )} \\
      Creates a new stealable task \\
    \texttt{\scriptsize parallel\_for( start, end, Functor iteration )} \\
      Executes iterations of a loop as stealable tasks that \\
      take the iteration index as an argument  \\
    \texttt{\scriptsize call\_on( core, Functor f )} \\ 
      Runs a limited function on a specific core without \\
      consuming a stack or context switching
	\end{tabular}
    \begin{minipage}{0.95\columnwidth}
      \caption{\label{fig:expressing-parallelism} \Grappa API: expressing parallelism
      } % \vspace{-4ex}}
    \end{minipage}
    %\vspace{-3ex}
  \end{center}
\end{figure}

>>>>

\paragraph{Workers} Workers execute application and system (e.g.,
communication) tasks. A worker is simply a collection of status bits and a
stack, allocated at a particular core. When a task is ready to execute it
is assigned to a worker, which executes the task functor on its own stack. 
Once a task is mapped to a worker it stays with that worker until it finishes.

\paragraph{Scheduling} During execution, a worker yields control of its core
whenever performing a long-latency operation, allowing the processor to
remain busy while waiting for the operation to complete. In addition, a
programmer can direct scheduling explicitly via the \Grappa API calls shown in
Figure~\ref{fig:scheduling}. To minimize yield overhead, the \Grappa scheduler
operates entirely in user-space and does little more than store state of one
worker and load that of another.
\TODO{mention how we block on response (``scheduler activations'' or whatever) not busy wait}

\TODO{either explain the usage of yield vs suspend in talking about
    short and longer latency tolerance or eliminate the
    distinction}
\begin{figure}[htbp]
  \begin{center}
  \begin{minipage}{0.95\columnwidth}  
  \begin{description}
    \item[\texttt{yield() }] \hfill \\
      Yields core to scheduler, enqueuing caller to be scheduled again soon
    \item[\texttt{wake( Worker * $w$ ) }] \hfill \\
      Enqueues some other worker $w$ to be scheduled again soon
    \item[\texttt{suspend() } ] \hfill \\
      Yields core to scheduler, enqueuing caller only once another task calls wake
	\end{description}
  \end{minipage}
    \begin{minipage}{0.95\columnwidth}
      \caption{\label{fig:scheduling} \Grappa scheduling API
      \TODO{Drop this? Doesn't seem non-obvious or important.}}
    \end{minipage}
  \end{center}
\end{figure}

@@

\begin{figure}[htbp]
  \begin{center}
	\begin{description}
    \item[\texttt{spawn( Functor f )}] \hfill \\
      Creates a new stealable task
    \item[\texttt{parallel\_for( start, end, Functor iteration )}] \hfill \\
      Executes iterations of a loop as stealable tasks that
      take the iteration index as an argument
    \item[\texttt{call\_on( core, Functor f )}] \hfill \\
      Runs a limited function on a specific core without
      consuming a stack or context switching
	\end{description}
    \begin{minipage}{0.95\columnwidth}
      \caption{\label{fig:expressing-parallelism} \Grappa API: expressing parallelism
      } % \vspace{-4ex}}
    \end{minipage}
    %\vspace{-3ex}
  \end{center}
\end{figure}
